---
title: "Assignment 04"
author: "Jarvis Sanders"
date: "9/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Problem #1

By graphing the data this way I am able to see that the sepal width data rises to a certain point and then decreases steadily after that with local peaks, but ultimately decreasing. 

For sepal length, the data increases and decreases often. Multiple local peaks and lows. 

```{r}
library(ggplot2)
library(dplyr)

ggplot(data = iris) +
  geom_bar(mapping = aes (x = Sepal.Length))

ggplot(data = iris) +
  geom_bar(mapping = aes (x = Sepal.Width))
```

<span style="color: green; font-size: 14pt">*Comments:*   </span>
  
  * <span style="color: green; font-size: 14pt">A bar plot is not really appropriate here; that would be useful for discrete (rather than continuous) data.  You are looking for a histogram, with some work on picking a reasonable bin width.  For example, see below.</span>
  * <span style="color: green; font-size: 14pt">Also be sure your final graphs have appropriate labels.</span>
   
    
```{r}
ggplot(iris) +
  geom_histogram(aes(x = Sepal.Length), binwidth = 0.5) +
  labs(title = "Alternate: Sepal Length Distribution", x = "Sepal Width", y = NULL)
```
    

Problem #2

By adding the categorical variable species, I am able to take a closer look at each species of flower such as the sepal length and width in one graph. 

```{r}
ggplot(data = iris) +
  geom_histogram(aes(x = Sepal.Length, fill = Species), binwidth = 1) +
  labs(title = "Species", 
       x = "Sepal Length",
       y = "Sepal Width")
```

<span style="color: green; font-size: 14pt">*Comments:*    </span>
        
  * <span style="color: green; font-size: 14pt">Your binwidth is a little large here; this gives you only five categories.  </span>
  * <span style="color: green; font-size: 14pt">Your y-axis is not width.  (You have not produced a graph for the distribution of widths here.)  </span>
  * <span style="color: green; font-size: 14pt">The color does help differentiate, but these are still hard to read plotted on top of each other.  It will help to separate the graphs by species with a `facet_wrap`, like below:
    </span>
    
```{r}
ggplot(data = iris) +
  geom_histogram(aes(x = Sepal.Length, fill = Species), binwidth = .45) +
  facet_wrap( ~ Species) +
  labs(title = "Alternate: Sepal Length by Species", 
       x = "Sepal Length",
       y = "Count")
```

Problem #3

By graphing the data this way, I will be able to see the relationship between the width of the sepal of virginica, as well as the count of each occurence. 

```{r}
ggplot(data = iris) +
  geom_histogram(mapping = aes (x = Sepal.Width, fill = "virginica"), binwidth = 1)
```

<span style="color: green; font-size: 14pt">*Comments:*  Again, this is too large of a binwidth.  (You only have three categories!)  What do you see about the distribution of this variable?
    </span>
